Magic Vs Evolution

### 2024-04-02 paper/paper.qmd
commiting the scripts

```{r}

darwin <-
  gutenberg_download(
    gutenberg_id = 2009,
    mirror = "https://gutenberg.pglaf.org/"
  )

@@

```{r}
harry <- pdf_text("../other/literature/HarryAzkaban.pdf")
class(harry)
harry <- tibble(
  raw_text = harry,
  page_number = c(1:454)
)

@@

```{r}
darwin <- read_csv(
  "../data/raw_data/darwin.csv",
  col_types = cols(
    gutenberg_id = col_integer(),
    text = col_character()
  )
)

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
```{r}
darwin_nature <-
  stan_glm(
    natural_count ~ word_count,
    data = darwin_reduced,
    family = poisson(link = "log"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )

@@

```{r}
plot_predictions(darwin_nature, condition = "word_count") +
  labs(x = "Number of words",
       y = "Average number of \"natural\"s in the first 10 lines") +
  theme_classic()
```
Negative relation it seems

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
darwin <-
  gutenberg_download(
    gutenberg_id = 2009,
    mirror = "https://gutenberg.pglaf.org/"
  )

@@

```{r}
#| echo: false
#| warning: false
#| message: false
harry <- pdf_text("../other/literature/HarryAzkaban.pdf")
class(harry)
harry <- tibble(
  raw_text = harry,
  page_number = c(1:454)
)

@@

```{r}
#| echo: false
#| warning: false
#| message: false
darwin <- read_csv(
  "../data/raw_data/darwin.csv",
  col_types = cols(
    gutenberg_id = col_integer(),
    text = col_character()
  )
)

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
```{r}
#| echo: false
#| warning: false
#| message: false
darwin_nature <-
  stan_glm(
    natural_count ~ word_count,
    data = darwin_reduced,
    family = poisson(link = "log"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )

@@

```{r}
#| echo: false
#| warning: false
#| message: false
plot_predictions(darwin_nature, condition = "word_count") +
  labs(x = "Number of words",
       y = "Average number of \"natural\"s in the first 10 lines") +
  theme_classic()
```
Negative relation it seems

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
```{r}
#| echo: false
#| warning: false
#| message: false
darwin_magic <-
  stan_glm(
    magic_count ~ word_count,
    data = darwin_reduced,
    family = poisson(link = "log"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )

saveRDS(
  darwin_magic,
  file = "../models/darwin_magic.rds"
)
```

```{r}
#| echo: false
#| warning: false
#| message: false
plot_predictions(darwin_magic, condition = "word_count") +
  labs(x = "Number of words",
       y = "Average number of \"magic\"s or \"miracle\"s appearing") +
  theme_classic()
```
As we can see here there is almost no correlation at all.

@@
